---
title: "GZM_SMA_factoranalysis"
author: "Michelle Byrne"
date: "2024-01-25"
output: html_document
---
This analysis is for cross-sectional data from the Gen Z Milestones Study
conducted in 2023 with young people aged 16-27 in Australia.
It is a factor analysis of the SMA-RSS questionnaire, and is based on the
following study, Kiekens, et al., 2023
https://doi.org/10.1007/s10508-022-02474-6

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include = F}
library(readr)
library(tidyverse)
library(lavaan)
library(semPlot)
library(reshape2)
library(dplyr)
library(Hmisc)
library(corrplot)
library(lmtest)
library(nlsem)
```

Combine the "concerned/anxious" and "likely" responses for each scenario. 
From Kiekens 2022: "Scores of anxious expectations were calculated for each 
item by multiplying the responses to the two questions, similar to other RS 
measures (Dyar et al.,2016; Pachankis et al., 2008).

```{r load data}
set.seed(123)
setwd("C:/")
GZMCore <- read.csv("Study One.csv")
```

```{r combine}
# Create new variable for analyses where only male and female SAB are included
GZMCore <- GZMCore %>%
  mutate(IdentitySexAnalysis = ifelse(IdentitySex %in% c(1, 2), IdentitySex, NA)) %>%
  mutate(IdentitySexAnalysis = factor(IdentitySexAnalysis))

# Subset the data
data_combined <- GZMCore[, c("AgeCurrent", "IdentitySexAnalysis",
                              "HSS1", "HSS2", "HSS3", "HSS4", "HSS5",
                              "HSS6", "HSS7", "HSS8", "HSS9", "HSS10",
                              "HSS11", "HSS12", "HSS13", "HSS14")]
```

# Original Exploration

Kiekens' models from 2022 indicated both a bifactor model fit best from an EFA,
but that unidimensionality was also supported. Below we test CFAs for both
1 and 2 factor models.

Kiekens 2022 explain that 
- *factor 1* "described scenarios in which someone was treated differently or excluded by others
without an explicit cue that this might be related to one’s sexual orientation (e.g., a situation where someone laughs when they pass you) and perpetrators were more often peers";
- *factor 2* "described scenarios in which there was a more explicit cue that sexual orientation
might play a role in whether someone would be excluded or treated differently (e.g., a situation involving a same-sex partner or a joke about LGBT people). Here, perpetrators were more often adults.

They also tested (with CFAs) both:
- a *bifactor model* - items allowed to load both on a general factor and 
2 group factors where all factor are orthogonal
- a *second-order model* - items load on orthogonal 1st order factors and 
those 1st order factors then load onto a general second-order factor;

## One-factor

```{r 1fCFA}
# 1 factor Model without covariances between items
f1_nocov <- "
RS =~ HSS1 + HSS2 + HSS3 + HSS4 + HSS5 + HSS6 + HSS7 + HSS8 + HSS9 + HSS10 + HSS11 + HSS12 + HSS13 + HSS14
"

# 1 factor Model with covariances between items (see note below)
f1_cov <- "
RS =~ HSS1 + HSS2 + HSS3 + HSS4 + HSS5 + HSS6 + HSS7 + HSS8 + HSS9 + HSS10 + HSS11 + HSS12 + HSS13 + HSS14

#Covariances
HSS1 ~~ HSS2 + HSS3 + HSS4 + HSS5 + HSS6 + HSS7 + HSS8 + HSS9 + HSS10 + HSS11 + HSS12 + HSS13 + HSS14
"

fit_f1_nocov <- cfa(f1_nocov, data = data_combined, missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f1_nocov, fit.measures = T, standardized = T)
fitmea_f1_nocov <- fitMeasures(fit_f1_nocov,
                              fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
semPaths(fit_f1_nocov)

# model with covariances was not identified, don't think we need them anyway:
# fit_f1_cov <- cfa(f1_cov, data = data_combined, missing = "ML", estimator = "MLR", se = "robust.mlr")
```

## Bifactor

```{r bifCFA}
# Bifactor Model without covariances between items
f2_nocov <- "
F1 =~ HSS1 + HSS2 + HSS3 + HSS4 + HSS5 + HSS6 + HSS7 + HSS8 
F2 =~ HSS9 + HSS10 + HSS11 + HSS12 + HSS13 + HSS14
"

fit_f2_nocov <- cfa(f2_nocov, data = data_combined, missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f2_nocov, fit.measures = T, standardized = T)
fitmea_f2_nocov <- fitMeasures(fit_f2_nocov,
                              fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
semPaths(fit_f2_nocov, whatLabels = "std", style = "ram", residuals = FALSE, intercepts = FALSE,
         layout = "tree", edge.color = "black", edge.width = 2, # Set edges to black and width to 1
         node.label.cex = 0.5, # Increase size of node labels
         edge.label.cex = 1, # Increase size of edge labels
         shapeMan = "square", sizeMan = 6, # Square shaped manifest nodes with increased size
         shapeLat = "ellipse", sizeLat = 7, # Elliptical latent nodes with increased size
         shapeInt = "triangle", sizeInt = 3, # Triangular intercept nodes with increased size
         edge.label.position = 0.75, # Adjust positions of edge labels
         nCharNodes = 4,
         mar=c(3,3,3,3))
```

## 2nd Order

```{r 2orCFA}
# Second order Model without covariances between items
f2order_nocov <- "
RS_f1 =~ HSS1 + HSS2 + HSS3 + HSS4 + HSS5 + HSS6 + HSS7 + HSS8 
RS_f2 =~ HSS9 + HSS10 + HSS11 + HSS12 + HSS13 + HSS14
RS_gen =~ RS_f1 + RS_f2
"

fit_f2order_nocov <- cfa(f2order_nocov, data = data_combined, missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f2order_nocov, fit.measures = T, standardized = T)
fitmea_f2order_nocov <- fitMeasures(fit_f2order_nocov,
                              fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
semPaths(fit_f2order_nocov)
```


The bifactor model performs the best. Taking these 6-items from the bifactor model, we ran sex-stratified CFAs using the bifactor model and compared the fit indices for the two groups as a sensitivity analysis given the larger proportion of assigned females at birth in the sample for Study One. 

# Six-item CFAs

```{r 1fCFA}
# 1 factor Model without covariances between items
f1_nocov <- "
RS =~ HSS1 + HSS2 + HSS4 + HSS9 + HSS10 + HSS11
"

# 1 factor Model with covariances between items (see note below)
f1_cov <- "
RS =~ HSS1 + HSS2 + HSS4 + HSS9 + HSS10 + HSS11

#Covariances
HSS1 ~~ HSS2 + HSS4 + HSS9 + HSS10 + HSS11
"

fit_f1_nocov <- cfa(f1_nocov, data = data_combined, missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f1_nocov, fit.measures = T, standardized = T)
fitmea_f1_nocov <- fitMeasures(fit_f1_nocov,
                              fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
semPaths(fit_f1_nocov)

# model with covariances was not identified, don't think we need them anyway:
# fit_f1_cov <- cfa(f1_cov, data = data_combined, missing = "ML", estimator = "MLR", se = "robust.mlr")
```

```{r bifCFA}
# Bifactor Model without covariances between items
f2_nocov <- "
RS_f1 =~ HSS1 + HSS2 + HSS4
RS_f2 =~ HSS9 + HSS10 + HSS11
"

fit_f2_nocov <- cfa(f2_nocov, data = data_combined, missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f2_nocov, fit.measures = T, standardized = T)
fitmea_f2_nocov <- fitMeasures(fit_f2_nocov,
                              fit.measures = c("cfi.scaled", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
semPaths(fit_f2_nocov)
```

```{r summary table}
# Extract fit measures for the bifactor model
fit_indices <- fitMeasures(fit_f2_nocov, fit.measures = c("cfi.scaled", "chisq.scaled", "pvalue.scaled", "rmsea.scaled", "srmr", "ecvi"))

# Create a formatted data frame for the fit indices
fit_indices_table <- data.frame(
  Measure = c("Scaled CFI", "Scaled Chi-Square", "P-value (Chi-Square)", "Scaled RMSEA", "Scaled SRMR", "ECVI"),
  Value = format(round(as.numeric(fit_indices), 4), nsmall = 4) # Format to 4 decimal places
)

# Print the table
print(fit_indices_table)
```

---
---

For further elaboration, we will run a sex-stratified and age-stratified CFA using the bifactor model as this was the best fit for the full sample. TO be thorough a 1 factor model will also be run for each.

```{r 1cfa sex-stratified raw}
# Split the data by sex (male = 1, female = 2)
male_data <- subset(data_combined, IdentitySexAnalysis == 1)
female_data <- subset(data_combined, IdentitySexAnalysis == 2)

# Fit the model for males
fit_f1_nocov_male <- cfa(f1_nocov, data = male_data, missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f1_nocov_male, fit.measures = TRUE, standardized = TRUE)
fitmea_f1_nocov_male <- fitMeasures(fit_f1_nocov_male, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))

# Fit the model for females
fit_f1_nocov_female <- cfa(f1_nocov, data = female_data, missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f1_nocov_female, fit.measures = TRUE, standardized = TRUE)
fitmea_f1_nocov_female <- fitMeasures(fit_f1_nocov_female, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
```

Below is a comparison of the fit measures for ASAB and AFAB for the 1 factor model.

```{r 1cfa sex-stratified comparison}
# Extract fit measures for male model
male_fit_measures <- fitMeasures(fit_f1_nocov_male, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))

# Extract fit measures for female model
female_fit_measures <- fitMeasures(fit_f1_nocov_female, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))

# Create a data frame for comparison
fit_comparison <- data.frame(
  Measure = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"),
  Male = as.numeric(male_fit_measures),
  Female = as.numeric(female_fit_measures)
)

# Print the comparison table
print(fit_comparison)
```

The 1 factor model shows a poor fit, lets look at the 2 factor model for the reduced 6-items.

```{r bifCFA sex-stratified male raw}
# Run the bifactor model for males
fit_f2_nocov_male <- cfa(f2_nocov, data = subset(data_combined, IdentitySexAnalysis == 1), missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f2_nocov_male, fit.measures = TRUE, standardized = TRUE)
fitmea_f2_nocov_male <- fitMeasures(fit_f2_nocov_male, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
```

```{r bifCFA sex-stratified female raw}
# Run the bifactor model for females
fit_f2_nocov_female <- cfa(f2_nocov, data = subset(data_combined, IdentitySexAnalysis == 2), missing = "ML", estimator = "MLR", se = "robust.mlr")
summary(fit_f2_nocov_female, fit.measures = TRUE, standardized = TRUE)
fitmea_f2_nocov_female <- fitMeasures(fit_f2_nocov_female, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
```

```{r bifCFA sex-stratified comparison}
# Extract fit measures for male model
male_fit_measuresbif <- fitMeasures(fit_f2_nocov_male, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
                                                                        
# Extract fit measures for female model
female_fit_measuresbif <- fitMeasures(fit_f2_nocov_female, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))

# Create a data frame for comparison
fit_comparisonbif <- data.frame(
  Measure = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"),
  Male = as.numeric(male_fit_measuresbif),
  Female = as.numeric(female_fit_measuresbif)
)

# Print the comparison table
print(fit_comparisonbif)
```

```{r age stratification}
# Split the data by age group
lower_age_data <- subset(data_combined, AgeCurrent <= 18)
upper_age_data <- subset(data_combined, AgeCurrent > 18)

# Run the bifactor model for 18 and under
fit_f2_nocov_lower_age <- cfa(f2_nocov, data = lower_age_data, missing = "ML", estimator = "MLR", se = "robust.mlr")

# Run the bifactor model for over 18
fit_f2_nocov_upper_age <- cfa(f2_nocov, data = upper_age_data, missing = "ML", estimator = "MLR", se = "robust.mlr")

# Extract fit measures for male model
lower_age_fit_measuresbif <- fitMeasures(fit_f2_nocov_lower_age, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))
                                                                        
# Extract fit measures for female model
upper_age_fit_measuresbif <- fitMeasures(fit_f2_nocov_upper_age, fit.measures = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"))

# Create a data frame for comparison
fit_comparisonage <- data.frame(
  Measure = c("cfi", "chisq.scaled", "pvalue.scaled", "df", "rmsea.scaled", "srmr", "ecvi"),
  lower = as.numeric(lower_age_fit_measuresbif),
  upper = as.numeric(upper_age_fit_measuresbif)
)

# Print the comparison table
print(fit_comparisonage)
```

```{r bifCFA age-stratified low raw}
# Run the bifactor model for males
summary(fit_f2_nocov_lower_age, fit.measures = TRUE, standardized = TRUE)
```

```{r bifCFA age-stratified high raw}
# Run the bifactor model for males
summary(fit_f2_nocov_upper_age, fit.measures = TRUE, standardized = TRUE)
```







